
%   \documentclass[defaultstyle]{thesis}
%   \documentclass[typewriterstyle]{thesis}
%   \documentclass[modernstyle]{thesis}
    \documentclass[modernstyle,12pt]{thesis}

%   \documentclass[modernstyle,11pt]{thesis}
%   \documentclass[defaultstyle,12pt]{thesis}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%    load any packages which are needed    %%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{latexsym}       % to get LASY symbols
\usepackage{epsfig}     % to insert PostScript figures
\usepackage{rotating}       % for sideways tables/figures
\usepackage{eufrak}
\usepackage{listofsymbols}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{morefloats}
\usepackage{placeins}


%%%%%%%%%%%%       all the preamble material:       %%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{\uppercase{Enhancement to XOS Operating System and XFS file system}}

\author{\uppercase{KRUTHIKA SURESH VED}} {\uppercase{B110300CS}} {\uppercase{SIKHA V MANOJ}} {\uppercase{B110572CS}} {\uppercase{SONIA V MATHEW}} {\uppercase{B110495CS}}


\degree{{\emph{\uppercase{Bachelor of Technology}}}}        %  #1 {long descr.}
    {B.Tech., Computer Science and Engineering}     %  #2 {short descr.}

\dept{Department of}            %  #1 {designation}
    {ComputerScience  And Engineering}      %  #2 {name}

\advisor{}{\uppercase{Dr. K Muralikrishnan}}           %  #1 {title}

\reader{Dr. K.A.Abdul Nazeer}      %  2nd person to sign thesis
%\readerThree{}        %  3rd person to sign thesis

\acknowledgements{  \OnePageChapter % *MUST* BE ONLY ONE PAGE!
We are highly indebted to \textbf{Dr. K.Muralikrishnan} for his guidance and constant supervision as well as for providing necessary information regarding the project and also for his support in completing the project.\\
We would like to express our gratitude towards \textbf{Dr. Abdul Naseer}, Head of Department of Computer Science and Engineering Department,  and  \textbf{Mrs. Lijiya A}, Project Coordinator, for their kind co-operation and encouragement which helped us in the completion of this project.\\
We thank the past contributors of the earlier versions of this project, Ajeet Kumar, Albin Suresh, Avinash, Deepak Goyal, Jeril K George, K Dinesh,Mathew Kumpalamthanam, Naseem Iqbal, Nitish Kumar, Ramnath Jayachandran, Sathyam Doraswamy, Shamil C M, Sreeraj S, Sumesh B, Vivek Anand T Kallampally, and Yogesh Mishra.\\
Our thanks and appreciations also goes to our colleagues in developing the project and people who have willingly helped us out with their abilities.\\
Last but not the least, we also wish to express our indebtedness to our parents as well as our family members whose blessings and support always helped us to face the challenges ahead. \\
\begin{raggedright}
\hspace*{75mm}\textbf{KRUTHIKA SURESH VED}\\
        \hspace*{75mm}\textbf{SIKHA V MANOJ}\\
\hspace*{75mm}\textbf{SONIA V MATHEW}\\
\end{raggedright}
    }

% a 1-page Table of Contents ??
 \ToCisShort

\abstract{  \OnePageChapter % one page only ??

    eXpOS or eXperimental Operating System is a tiny multiprogramming operating system. It has a very simple specification that allows a junior undergraduate computer science student to implement it in a few months, subject to availability of adequate hardware and programming platform support. It is also an instructional tool to learn and implement OS data structures and functionalities on a simulated machine called XSM (eXperimental String Machine).
    }

\LoSisShort
\emptyLoS % no List of Symbols at all ??

\LoFisShort % a 1-page List of Figures ??
% \emptyLoF % no List of Figures at all ??

\LoTisShort % a 1-page List of Tables ??
% \emptyLoT % no List of Tables at all ??
\LoAisShort
%\LoA
 \emptyLoA % no List of Abbreviations at all ??
%\emptyLos  % no List of symbols
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%       BEGIN DOCUMENT...         %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%  Weird footnotes??
%%%%  default=\arabic; \roman, \Roman, \alph, \Alph, \fnsymbol
%   \renewcommand{\thefootnote}{\fnsymbol{footnote}}
%   \setcounter{footnote}{0}
\begin{document}

\input macros.tex
\input ch1.tex
\input lit_survey.tex
\input ch2.tex
\input ch3.tex
\input ch4.tex
\input ch5.tex
\input ch6.tex
\input ch7.tex
\input ch8.tex
\input ch9.tex
\input ch10.tex
%% all chapters can be input like this....%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%  Bibliography %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{plain}   % or "siam", or "alpha", or "abbrv"
                % see other styles in
                % /usr/local/TeX/texmf/bibtex/bst

\nocite{*}      % list all refs in database, cited or not.


\begin{thebibliography}{30}
\bibitem {1}
Saman Hadiani, Niklas Dahlbäck, and Uwe Assmann, "Nachos Beginner's Guide", \texttt{$http://www.ida.liu.se/~TDDB63/material/begguide/$}
\bibitem {2}
George Fankhauser, Christian Conrad, Eckart Zitzler, Bernhard Plattner, "Topsy - A Teachable Operating System", Version 1.1, \texttt{$http://www.tik.ee.ethz.ch/~topsy/Book/Topsy_1.1.pdf$}
\bibitem {3}
Shamil C. M., Sreeraj S, and Vivek Anand T.Kallampally, "XOS - An Experimental Operating System", \texttt{$http://xosnitc.github.io/$}
\bibitem {4}
Maurice J. Bach, "The Design of Unix Operating System"
\end{thebibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%  Appendices %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\appendix   % don't forget this line if you have appendices!
\input appB.tex
%% all appendices included in this manner%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%   THE END   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}
